---
title: 'Outcome Analysis in MRD+ positive patients at End of Intestification'
author: "Jenny Smith"
date: "June 14, 2018"
output: html_document
---

```{r setup}
library(knitr)
knitr::opts_chunk$set(tidy.opts=list(width.cutoff=50),tidy=TRUE, fig.align='center', fig.width = 10, fig.height = 10)
knitr::opts_knit$set(root.dir = '/fh/fast/meshinchi_s/workingDir/TARGET/AML_TARGET/Clinical/analysis/2018.06.14_outcome_MRD+_EOIntens')
```


```{r message = FALSE, warning=FALSE}
library(stringr)
library(magrittr)
library(ggplot2)
library(dplyr)
library(tibble)
library(tidyr)
getwd()
```

```{r}
source("~/scripts/survival_analysis/Survplot_Functions_2017.03.31.r")
```


#Read in the Clinical Data

```{r}
CDE.1031 <- read.csv("~/reference_mapping-files/TARGET_AML_1031_CDE_cleaned_6.15.2018.csv", 
                     stringsAsFactors = FALSE)

# head(CDE.1031[,1:5])
# dim(CDE.1031)
```


```{r}
Intens <- read.csv("~/reference_mapping-files/AAML1031All MRD at EO Intensification.csv", 
                   stringsAsFactors = FALSE)


Intens <- Intens %>%
  #Collapsed.classification is considering any patients with detectable MRD as Positive. 
  #Classification.End.of.Intensification.1 as MRD+ is greater than or equal to 0.1
  mutate(Collapsed.Classification=gsub("Neg.+", "Negative",
                                       gsub("Positive .+", "Positive", Classification.End.of.Intensification.1)), 
         Classification.End.of.Intensification.1=gsub("Neg.+", "Negative", Classification.End.of.Intensification.1)) 

# dim(Intens) #787
# head(Intens[,1:5])
```


```{r}
table(Intens$Classification.End.of.Intensification.1)
table(Intens$Collapsed.Classification)
```


```{r}
Intens.SurvData <- Intens %>% 
  inner_join(.,select(CDE.1031, everything()),
             by=c("cogname"="Patient.registration.number")) %>% 
  filter(Classification.End.of.Intensification.1 != "Inadequate") %>%
  filter(SCT.in.1st.CR != "Unknown") %>% 
  mutate(X=rep("AML", nrow(.))) %>%
  droplevels(.) 

# head(Intens.SurvData[,1:5]) #650 patients
# dim(Intens.SurvData)
```

```{r}
addmargins(table(Intens.SurvData$Classification.End.of.Intensification.1, Intens.SurvData$OS.event.ID,
                 useNA = "always"))
```

```{r}
addmargins(table(Intens.SurvData$Collapsed.Classification, Intens.SurvData$OS.event.ID,
                 useNA = "always"))
```

```{r}
table(Intens.SurvData$SCT.in.1st.CR, Intens.SurvData$Classification.End.of.Intensification.1) #87 in SCT 
table(Intens.SurvData$SCT.in.1st.CR, Intens.SurvData$Collapsed.Classification) #87 in SCT 
```

There were only 20 patients who were positive for MRD at the end of intesification 1 and went into SCT. 


Classification.End.of.Intensification.1
Collapsed Classification

MRD.at.end.of.course.1
MRD.at.end.of.course.2

Patients who are
1) MRD+ at CR1, MRD+ at CR2, and MRD+ EOInt
2) MRD+ at CR1, MRD+ at CR2, and MRD- at EOInt
3) MRD+ at CR1, MRD- at CR2, and MRD- at EOInt

```{r}
cohort3 <- Intens.SurvData %>%
  filter(MRD.at.end.of.course.1 != "Unknown") %>%
  filter(MRD.at.end.of.course.2 != "Unknown") %>% 
  mutate(MRD.at.end.of.course.1=ifelse(MRD.at.end.of.course.1 == "Yes", ))

dim(cohort3) #602 patients
table(cohort3$MRD.at.end.of.course.1)
table(cohort3$MRD.at.end.of.course.2)
```

Postive at CR1 = 106 patients
- 21 patient positive at CR2 and positve at EOInt
- 11 patients negative at CR2 


```{r}
table(cohort3$Collapsed.Classification, cohort3$MRD.at.end.of.course.2, cohort3$MRD.at.end.of.course.1)
```








#OS and EFS

##SCT +/- 

```{r}
KM.SCT <- KM.plots(df=Intens.SurvData, groupBy = "X", type="OS", covariate = "SCT.in.1st.CR", cohort = "1031")

KM.SCT
# saveMultiPlots(KM.SCT)
```

```{r}
KM.SCT$OS
KM.SCT$EFS
```


## MRD+ with and without SCT

```{r}
# subset(Intens.SurvData, Collapsed.Classification == "Positive")
KM.MRD_inSCT <- KM.plots(df=Intens.SurvData, 
                         groupBy = "Collapsed.Classification", 
                         type="OS", 
                         covariate = "SCT.in.1st.CR", 
                         cohort="1031")

KM.MRD_inSCT
# saveMultiPlots(KM.MRD_inSCT)
```

```{r}
KM.MRD_inSCT$OS
KM.MRD_inSCT$EFS
```



## All the Patient MRD Groups (not inadequate)
```{r}
KM.MRD_bySCT <- KM.plots(df=Intens.SurvData, 
                   groupBy = "SCT.in.1st.CR",
                   type = "OS", 
                   covariate = "Classification.End.of.Intensification.1", 
                   cohort = "1031")

KM.MRD_bySCT
# saveMultiPlots(KM.plots.res = KM.MRD_bySCT,w=10)
```

```{r fig.height=5, fig.width=10}
KM.MRD_bySCT$OS
```


```{r fig.height=5, fig.width=10}
KM.MRD_bySCT$EFS
```


##Any MRD considered to be MRD positive

```{r}
KM.MRD_bySCT.2 <- KM.plots(df=Intens.SurvData, 
                   groupBy = "SCT.in.1st.CR",
                   type = "OS", 
                   covariate = "Collapsed.Classification", 
                   cohort = "1031")

KM.MRD_bySCT.2
# saveMultiPlots(KM.plots.res = KM.MRD_bySCT.2,w=10)
```

```{r fig.height=5, fig.width=10}
KM.MRD_bySCT.2$OS
```


```{r fig.height=5, fig.width=10}
KM.MRD_bySCT.2$EFS
```


#Relapse Risk of the MRD+/- in SCT

```{r}
library(survival)
library(cmprsk)
```

```{r}

```


```{r}
cumInc.MRD <- Intens.SurvData %>% 
  # group_by(Classification.End.of.Intensification.1) %>% 
  do(cumIncidence=cuminc(ftime = .$EFS.time..days., 
                         fstatus = .$EFS.event.type.ID, 
                         group = .[,"Classification.End.of.Intensification.1"], 
                         rho=0, 
                         cencode="Censored"))

cumInc.MRD
```

```{r}
plot(cumInc.MRD$cumIncidence[[1]], color = brewer.pal(9, "Set1"), lwd=3)
```



```{r}
cumulativeInc.Reg <- function(df, groupBy, covariate, cohort, cc=NULL){
  if (cohort == "0531"){
    
  }
}
```


```{r}
cumIncGO <- CDE.0531.Go %>%
  group_by(rs12459419) %>%
  do(cumIncidence=cuminc(ftime=.$Event.Free.Survival.Time.in.Days, 
                         fstatus=.$First.Event,
                         group=.$GO.Treatment,
                         rho=0,
                         cencode = "Censored"), 
     compRiskReg=crr(ftime = .$Event.Free.Survival.Time.in.Days, 
                  fstatus= .$First.Event,
                  cov1 = matrix(.$Num.GO.Treatment, dimnames = list(NULL,"GO.Trt")), 
                  failcode = "Relapse", 
                  cengroup = "Censored"))
```




#Examine the Clinical Characteristics of the 20 MRD+ in SCT

```{r message=FALSE}
library(compareGroups)
```

```{r}
SCT <- Intens.SurvData %>%
  filter(SCT.in.1st.CR == "Yes") %>%
  select(USI,3, 15:18,25:26, 65, 54, 55,57:58,33:50)

# head(SCT[,1:5])
```


```{r}
dim(SCT)
table(SCT$Classification.End.of.Intensification.1)
```


```{r warning=FALSE}
comp <- compareGroups(Classification.End.of.Intensification.1 ~ ., data = SCT[,-1], 
                      method=4, Q1=0, Q3=1)

```

```{r}
tab <- createTable(comp)
```

```{r}
tab
# export2csv(tab, "TARGET_AML_1031_MRDpositive_vs_MRDnegative_inSCT_ClinicalCharacteristics_Table.csv")
```


#Session Information 

```{r}
sessionInfo()
```

